A Web Application for Wildlife Sightings - how accessible is this technology using modern frameworks?

### 2024-12-17 article/main.tex
update main.tex to include links to frontend and backend repositories; clarify the open-source nature of the code

\subsection{Code Base}
All the code for the app is publicly available on GitHub. 
\begin{itemize}
    \item Frontend: \url{https://github.com/juliankraft/WildtierSichtungsApp_front}
    \item Backend: \url{https://github.com/juliankraft/WildtierSichtungsApp_back}
\end{itemize}

>>>>

\subsection{Code Base}
All the code for the app is publicly available on GitHub:
\begin{itemize}
    \item Frontend: \url{https://github.com/juliankraft/WildtierSichtungsApp_front}
    \item Backend: \url{https://github.com/juliankraft/WildtierSichtungsApp_back}
\end{itemize}

It is worth mentioning that the code is not perfect -- at this point it is not more than a working prototype. Still the code is open source and can
be used by anyone to do whatever under the creative commons license CC0 1.0 Universal.
